---
title: "PS07"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

# Setup
```{r}
# Load necessary Packages
library(ggplot2)
library(dplyr)
library(gapminder)

# Data wrangling for 'gapminder' data frame
gapminder2007 <- gapminder %>%
  filter(year == 2007) %>%
  select(country, lifeExp, continent, gdpPercap)
```

## Including Plots

You can also embed plots, for example:

## Creating a data visualisation

```{r pressure, echo=FALSE}
ggplot(gapminder2007, aes(x = continent, y = gdpPercap)) +
  geom_boxplot() +
  labs(
    x = "Continent", y = "GPD per capita",
    title = "GDP by continent"
  )
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
